% Change the size of the paper your CV will be printed on
% by entering either a4paper or letterpaper here.
\documentclass[a4paper]{Resume}

\usepackage[x11names]{xcolor}
% Set color of body text
\color{black}

\usepackage{Sweave}
\begin{document}
\input{Resume-concordance}
	
% Set page colour using X11names colour definitions
\setPageColour{white}

% Set header details being aligned to the right or left
% If an image is displayed it will be shown on the
% opposite side to what is set here.
\setHeaderAlignment{left}

% Set colour of all headings, header highlights
\setHeadingColours{SlateGray3}

% Set image file to be displayed in header
% If left blank no image is displayed
%\setImage{profilepic.jpg}

% If image not being displayed then user can
% move contact details to opposite side of
% page to name and jobtitle.
% Use either opposite or below
\setContactLocation{opposite}

% Set up information needed for header.
% If you do not want to include certain
% information use {} instead. 
\setYourName{Patrick Harned}
\setYourJobTitle{Data Scientist/ML Engineer}
\setYourMobileNo{347-263-0441}
\setYourEmailAddr{pwharned@gmail.com}
\setYourWebAddr{pwharned.github.io/Resume/}

% Display header information 
\showHeader

% Set up whether section headings are on the left or right
\setSectionAlignment{left}

% Creates a new section title / heading

\personalStatement{Machine Learning Engineer and Data Scientist with experience building end-to-end containerized analytics and AI applications. Extensive knowledge of embedded database programming, database optimization, cloud-native development and Hadoop.}

\newHeading{Competencies}

% Add up to nine core skills. If they are
% all not needed use {} instead.
\addSkills{Scala}
		  {Python}
		  {R}
		  {C/C++}
		  {SQL}
		  {Linux}
		  {IBM Cloud/AWS}
		  {Docker/Kubernetes/Openshift}
		  {Hadoop}
		  
\newHeading{Career Summary}

% Set up whether job title or company printed first
% Either use JobFirst or CompanyFirst
\setJobCompanyOrder{JobFirst}

% This displays the whole of the role information
% including dates [1], job title [2],
% company name [3] and role summary [4]
% If a full history is required use \newrole and \roleAchievements
% If only a brief description needed then just use \newrole
\newRole{2021 -- present}
        {Data Scientist}
        {IBM Expert Labs}
        {Build and deploy cloud-native AI solutions on IBM Cloud Paks and Red Hat Openshift for enterprise clients.}
        \newline


\roleAchievements{Develop end-to-end model risk management solutions for AI based applications. Develop and deploy Spark applications for MRM on high volume ML models.}
{Develop Kerberos authentication API for authenticating containerized Spark jobs to remote Hadoop environments (Hive, HDFS) to support batch scoring of Spark models.}
{Developed Scala APIs for exposing NoSQL datastores to visualization layers to provide analytics to LOB for OCP cluster provisioning application.}
{Designed stress tests for containerized MRM applications - identified and closed application performance gaps.}
{Developed embdedded database applications for performing embdedded database machine learning to support model drift and explainabilty analysis on federated data.}
{Developed Gitops workflows with ArgoCD/Terraform to automate provisioning of Openshift clusters and application deployments.}


\newRole{2019 -- 2020}
{Data Scientist}
{IBM Cloud Pak Acceleration Team}
{Build AI solutions on IBM Cloud Paks and Openshift. Deploy to various cloud providers (AWS/Azure/IBM Cloud)}

\roleAchievementsthree{Developed federated DB2 data warehouse for merging JSON and tabular data source from external APIs and remote databases (Hive, MySQL, Postgres).}
{Developed Scala and Python microservices for integrating analytics applications with federated authentication services.}
{Developed and deployed custom ML models (Scala/Akka) for customer ranking and churn prediction.}


\newRole{2018 -- 2019}
{Data Specialist}
{Princeton University}
{Assist research team in producing visualizations, data validation and data quality pipelines, and conducting statistical analysis of Arab Barometer survey data.}

\roleAchievementsthree{Design and deploy data quality monitoring pipelines in R and Python.}
{Build pipleines for cleanining and managing Arab Barometer survey data to support automated data cleaning.}
{Build dashboards, reporting and analytics pipelines. Conducted statistical analysis of Arab Barometer data and contributed to research.}


% move, duplicate, delete or comment out the following line if necessary
% This is training you have done in your own time


% School education
\newHeading{Education}
         
\newCourse{2019}{Dual Masters of Global Policy Studies and Middle Eastern Studies}{University of Texas at Austin}{}
\newCourse{2015}{Bachelors of Arts, Classical Langauges}{Hunter College, City University of New York}{}

\newHeading{Languages}
\addLanguages{Native English, Professional Fluency in Arabic,}
		  {Conversational  in Japanese,}
		  {German,}
		  {French and}
		  {Turkish}
          
\clearpage


 

\end{document}
