% Change the size of the paper your CV will be printed on
% by entering either a4paper or letterpaper here.
\documentclass[a4paper]{Resume}

\usepackage[x11names]{xcolor}
% Set color of body text
\color{black}

\usepackage{Sweave}
\begin{document}
\input{Resume-concordance}
	
% Set page colour using X11names colour definitions
\setPageColour{white}

% Set header details being aligned to the right or left
% If an image is displayed it will be shown on the
% opposite side to what is set here.
\setHeaderAlignment{left}

% Set colour of all headings, header highlights
\setHeadingColours{SlateGray3}

% Set image file to be displayed in header
% If left blank no image is displayed
%\setImage{profilepic.jpg}

% If image not being displayed then user can
% move contact details to opposite side of
% page to name and jobtitle.
% Use either opposite or below
\setContactLocation{opposite}

% Set up information needed for header.
% If you do not want to include certain
% information use {} instead. 
\setYourName{Patrick Harned}
\setYourJobTitle{Technical Solution Architect/Full Stack Enginner}
\setYourMobileNo{347-263-0441}
\setYourEmailAddr{pwharned@gmail.com}
\setYourWebAddr{pwharned.github.io/Resume/}

% Display header information 
\showHeader

% Set up whether section headings are on the left or right
\setSectionAlignment{left}

% Creates a new section title / heading

\personalStatement{I am a Solutions Architect and Full Stack Engineer with experience building end-to-end ML solutions for clients.}

 \newHeading{}

% Add up to nine core skills. If they are
% all not needed use {} instead.
\begin{minipage}{.25\textwidth}
  \textcolor{\HeadingColour}{\robotoThin{\textbf{\large{Languages}}}}
  \vspace{1em}
  \begin{itemize}
  \item{Scala/Java}
  \item{Python}
  \item{C/C++}
  \item{Go}
  \item{Rust}
  
  \end{itemize}
\end{minipage}% This must go next to `\end{minipage}`
\begin{minipage}{.25\textwidth}
  \textcolor{\HeadingColour}{\robotoThin{\textbf{\large{Frameworks}}}}
  \vspace{1em}
    \begin{itemize}
  \item{Pandas/Sklearn}
  \item{Zio}
  \item{SparkMMLib}
  \item{PyTorch}
  \item{React}
  
  \end{itemize}
\end{minipage}% This must go next to `\end{minipage}`
\begin{minipage}{.25\textwidth}
  \textcolor{\HeadingColour}{\robotoThin{\textbf{\large{Platforms}}}}
  \vspace{1em}
    \begin{itemize}
  \item{Hadoop/Spark}
  \item{Kubernetes/Openshift}
  \item{AWS/GCP}
  \item{Linux}
  \item{Docker}
  
  \end{itemize}
\end{minipage}% This must go next to `\end{minipage}`
\begin{minipage}{.25\textwidth}
  \textcolor{\HeadingColour}{\robotoThin{\textbf{\large{Skills}}}}
  \vspace{1em}
    \begin{itemize}
  \item{Machine Learning}
  \item{Gen AI}
  \item{Analytics/Big Data}
  \item{NLP}
  \item{Embedded Systems}
  
  \end{itemize}
\end{minipage}


\newHeading{Career Summary}

% Set up whether job title or company printed first
% Either use JobFirst or CompanyFirst
\setJobCompanyOrder{JobFirst}

% This displays the whole of the role information
% including dates [1], job title [2],
% company name [3] and role summary [4]
% If a full history is required use \newrole and \roleAchievements
% If only a brief description needed then just use \newrole
\newRole{2021 -- present}
        {Data Scientist}
        {IBM Expert Labs}
        {Build and deploy cloud-native AI solutions on IBM Cloud Paks and Red Hat Openshift for enterprise clients. Collaborate with product management and various stakeholders across IBM and enterprise clients to build high value add solutions and drive AI adoption.}
        \newline


\roleAchievements{Led development of Retrieval-Augmented Generation powered customer support agent using IBM Granite foundation Models. Integrated GoLang backend with ElasticSearch vector database to support multimedia search and automated FAQ generation. Integrated IBM Carbon React  front\-end interface with IBM Sterling OMS and Watson Assistant. Developed comprhensive testing framework for LLM prompt validation and tuning. }
{Implemented GPU monitoring platform for tracking LLM workloads on on-prem NVIDIA hardware using Prometheus, Db2, Scala and WatsonX integrations.}
{Train and deploy BERT entity-extraction models to automate coding for clinical pathways program. Drove automation of clinical tasks with improved accuracy for NHS partner hospitals.}
{Develop applications for performing embdedded database machine learning to support model drift and explainabilty analysis on federated data. Collaborate with UIX teams to distill complex findings into actionable insights. }
{Develop federated data platform for tracking bias across machine learning models deployed to Google Cloud using Watson Query and React. }


\newRole{2019 -- 2020}
{Data Scientist}
{IBM Cloud Pak Acceleration Team}
{Build AI solutions on IBM Cloud Paks and Openshift. Deploy to various cloud providers (AWS/Azure/IBM Cloud)}

\roleAchievementsthree{Developed federated DB2 data warehouse for merging JSON and tabular data source from external APIs and remote databases (Hive, MySQL, Postgres).}
{Developed Scala and Python microservices for integrating analytics applications with federated authentication services. Developed federated data platform in Db2 for tracking performance of ML models for large retailer.}
{Proposed and implemented ML driven solutions for tracking COVID data for public client. Produced human-readable visualizations of model predictions to enabled stakeholder action. Manage enterprise Openshift and Cloud Pak for Data clusters.}


\newRole{2018 -- 2019}
{Data Specialist}
{Princeton University}
{Assist research team in producing visualizations, data validation and data quality pipelines, and conducting statistical analysis of Arab Barometer survey data.}

\roleAchievementsthree{Design and deploy data quality monitoring pipelines in R and Python. Build regression and RandomForest models to analyze survey data and contribute to original research. Perform statistical analysis and quality analysis of survey data. Provide Arabic-English translation assistance.}
{Build pipleines for cleanining and managing Arab Barometer survey data to support automated data cleaning.}
{Build dashboards, reporting and analytics pipelines. Conducted statistical analysis of Arab Barometer data and contributed to research.}


% move, duplicate, delete or comment out the following line if necessary
% This is training you have done in your own time


% School education
\newHeading{Education}
         
\newCourse{2019}{Dual Masters of Global Policy Studies and Middle Eastern Studies}{University of Texas at Austin}{}
\newCourse{2015}{Bachelors of Arts, Classical Langauges}{Hunter College, City University of New York}{}

\newHeading{Languages}
\addLanguages{Native English, Professional Fluency in Arabic,}
		  {Conversational  in Japanese,}
		  {German,}
		  {French and}
		  {Turkish}
          
\clearpage


 

\end{document}
